---
title: "STA 160 Project"
author: "Austin Chen"
date: "4/13/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install.packages("ggplot2")
#install.packages("tidyverse")
Kinematics_Data <- read.csv("~/Desktop/STA 160/Kinematics_Data.csv")
Kinematics_Data$activity = as.factor(Kinematics_Data$activity)
View(Kinematics_Data)
```

summaries of columns
missing values



```{r}
summary(Kinematics_Data)
```

```{r}
sum(is.na(Kinematics_Data))
```

No NA values

We have no missing values and data cleaning isn't necessary.

```{r}
wrist_activity = cbind.data.frame(Kinematics_Data$wrist, Kinematics_Data$activity)
wrist_activity_table = table(wrist_activity)
wrist_activity_table
```

Walking and right wrist combination happens the most. 

```{r}
test = chisq.test(wrist_activity_table)
eij = test$expected
test
eij

```


In the chi-squared test for independence, at alpha = 0.05, we can conclude that wrist and activity are dependent of each other. We will investigate this further. 

```{r}
#correlation
subset = Kinematics_Data[ , c("acceleration_x", "acceleration_y", "acceleration_z", "gyro_x", "gyro_y", "gyro_z")]   
cor(subset)
```

```{r}
#install.packages("scales")
library(tidyverse)
ggplot(Kinematics_Data, 
       aes(x = acceleration_x , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "Acceleration_x by activity")
```

# guesses
x is side by side
y is forward or backwards
z is up and down

add mean lines on plot
study effect of wrist


```{r}
ggplot(Kinematics_Data, 
       aes(x = acceleration_y , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "Acceleration_y by activity")
```

```{r}
ggplot(Kinematics_Data, 
       aes(x = acceleration_z , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "Acceleration_z by activity")
```

```{r}
ggplot(Kinematics_Data, 
       aes(x = gyro_x , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "gyro_x by activity")
```

```{r}
ggplot(Kinematics_Data, 
       aes(x = gyro_y , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "gyro_y by activity")
```


```{r}
ggplot(Kinematics_Data, 
       aes(x = gyro_z , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "gyro_z by activity")
```

```{r}
#install.packages("scatterplot3d") # Install
library("scatterplot3d") # load
colors <- c("blue", "red")
colors <- colors[as.numeric(Kinematics_Data$activity)]
scatterplot3d(Kinematics_Data$gyro_x,Kinematics_Data$gyro_y,Kinematics_Data$gyro_z, color = colors)
legend("right",legend = c("walking", "running"),
      col =  c("blue", "red"), pch = 6)
```

```{r}
colors <- c("blue", "red")
colors <- colors[as.numeric(Kinematics_Data$activity)]
scatterplot3d(Kinematics_Data$acceleration_x,Kinematics_Data$acceleration_y,Kinematics_Data$acceleration_z, color = colors)
legend("right",legend = c("walking", "running"),
      col =  c("blue", "red"), pch = 6)
```

```{r}
colors <- c("blue", "red")
colors <- ifelse(Kinematics_Data$wrist == 0, "blue", "red")
scatterplot3d(Kinematics_Data$acceleration_x,Kinematics_Data$acceleration_y,Kinematics_Data$acceleration_z, color = colors)
legend("right",legend = c("left wrist", "right wrist"),col =  c("blue", "red"), pch = 6)
```

```{r}
colors <- c("blue", "red")
colors <- ifelse(Kinematics_Data$wrist == 0, "blue", "red")
scatterplot3d(Kinematics_Data$gyro_x,Kinematics_Data$gyro_y,Kinematics_Data$gyro_z, color = colors)
legend("right",legend = c("left wrist", "right wrist"),col =  c("blue", "red"), pch = 6)
```

## Data and plots for left wrist and walking

```{r}
zerozero_data = Kinematics_Data[Kinematics_Data['wrist'] == 0 & Kinematics_Data['activity'] == 0,]
zerozero_data
```

```{r}
summary(zerozero_data)
```

```{r}
#install.packages("scales")
library(tidyverse)
ggplot(zerozero_data, 
       aes(x = acceleration_x , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "Acceleration_x by activity on left wrist")
```




```{r}
ggplot(zerozero_data, 
       aes(x = acceleration_y , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "Acceleration_y by activity on left wrist")
```

```{r}
ggplot(zerozero_data, 
       aes(x = acceleration_z , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "Acceleration_z by activity on left wrist")
```

```{r}
ggplot(zerozero_data, 
       aes(x = gyro_x , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "gyro_x by activity on left wrist")
```

```{r}
ggplot(zerozero_data, 
       aes(x = gyro_y , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "gyro_y by activity on left wrist")
```


```{r}
ggplot(zerozero_data, 
       aes(x = gyro_z , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "gyro_z by activity on left wrist")
```



## Data and plots for right wrist and walking 

```{r}
onezero_data = Kinematics_Data[Kinematics_Data['wrist'] == 1 & Kinematics_Data['activity'] == 0,]
onezero_data
```

```{r}
summary(onezero_data)
```


```{r}
#install.packages("scales")
library(tidyverse)
ggplot(onezero_data, 
       aes(x = acceleration_x , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "Acceleration_x by activity on right wrist")
```



```{r}
ggplot(onezero_data, 
       aes(x = acceleration_y , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "Acceleration_y by activity on right wrist")
```

```{r}
ggplot(onezero_data, 
       aes(x = acceleration_z , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "Acceleration_z by activity on right wrist")
```

```{r}
ggplot(onezero_data, 
       aes(x = gyro_x , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "gyro_x by activity on right wrist")
```

```{r}
ggplot(onezero_data, 
       aes(x = gyro_y , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "gyro_y by activity on right wrist")
```


```{r}
ggplot(onezero_data, 
       aes(x = gyro_z , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "gyro_z by activity on right wrist")
```



## Data and plots for left wrist and running


```{r}
zeroone_data = Kinematics_Data[Kinematics_Data['wrist'] == 0 & Kinematics_Data['activity'] == 1,]
zeroone_data
```

```{r}
summary(zeroone_data)
```

```{r}
#install.packages("scales")
library(tidyverse)
ggplot(zeroone_data, 
       aes(x = acceleration_x , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "Acceleration_x by activity on left wrist")
```



```{r}
ggplot(zeroone_data, 
       aes(x = acceleration_y , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "Acceleration_y by activity on left wrist")
```

```{r}
ggplot(zeroone_data, 
       aes(x = acceleration_z , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "Acceleration_z by activity on left wrist")
```

```{r}
ggplot(zeroone_data, 
       aes(x = gyro_x , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "gyro_x by activity on left wrist")
```

```{r}
ggplot(zeroone_data, 
       aes(x = gyro_y , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "gyro_y by activity on left wrist")
```


```{r}
ggplot(zeroone_data, 
       aes(x = gyro_z , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "gyro_z by activity on left wrist")
```


## Data and plots for right wrist and running


```{r}
oneone_data= Kinematics_Data[Kinematics_Data['wrist'] == 1 & Kinematics_Data['activity'] == 1,]
oneone_data
```

```{r}
summary(oneone_data)
```

```{r}
#install.packages("scales")
library(tidyverse)
ggplot(oneone_data, 
       aes(x = acceleration_x , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "Acceleration_x by activity on right wrist")
```


```{r}
ggplot(oneone_data, 
       aes(x = acceleration_y , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "Acceleration_y by activity on right wrist")
```

```{r}
ggplot(oneone_data, 
       aes(x = acceleration_z , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "Acceleration_z by activity on right wrist")
```

```{r}
ggplot(oneone_data, 
       aes(x = gyro_x , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "gyro_x by activity on right wrist")
```

```{r}
ggplot(oneone_data, 
       aes(x = gyro_y , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "gyro_y by activity on right wrist")
```


```{r}
ggplot(oneone_data, 
       aes(x = gyro_z , 
           fill = activity)) +
  geom_density(alpha = 0.4) +
  labs(title = "gyro_z by activity on right wrist")
```










